% Draft #1 (final?)

\vfil

\centerline{\Large Computer Science Project Proposal}
\vspace{0.4in}
\centerline{\Large How to write a dissertation in \LaTeX\ }
\vspace{0.4in}
\centerline{\large C. Diamand, King's College}
\vspace{0.3in}
\centerline{\large Originator: Dr David Chisnall}
\vspace{0.3in}
\centerline{\large 23$^{rd}$ October 2014}

\vfil

\noindent
{\bf Project Supervisor:} Dr David Chisnall
\vspace{0.2in}

\noindent
{\bf Director of Studies:} Dr Timothy Griffin
\vspace{0.2in}
\noindent

\noindent
{\bf Project Overseers:} Prof Marcelo Fiore \& Prof Ian Leslie

% Main document

\section*{Introduction, The Problem To Be Addressed}

  Many students write their CST dissertations in \LaTeX\ and spend a fair
  amount of time learning just how to do that. The purpose of this project is
  to write a demonstration dissertation that explains in detail how it done.

  This core proposal document will be augmented by a separately-printed cover
  sheet at the front and a resource form at the end.  Additional sheets for
  risk assessment and human resources may also need to be included.

  This document will repeat much of the material that is summarised on the
  additional sheets.

\section*{Starting Point}

  {\em Describe existing state of the art, previous work in this area,
  libraries and databases to be used.  Describe the state of any existing
  codebase that is to be built on.  }

  I am already able to write prose using the English language. I have an online
  dictionary. etc..

\section*{Resources Required}

  {\em A note of the resources required and confirmation of access.}

  For this project I shall mainly use my own quad-core computer that runs
  Fedora Linux. Backup will be to github and/or to an SVN repository on an
  external hard disk that is dumped to writable CD/DVD media.  I have another
  similar computer to hand should my main machine suddenly fail.  I require no
  other special resources.

\section*{Work to be done}

  {\em Describe the technical work.}

  The project breaks down into the following sub-projects:

  \begin{enumerate}
    \item The construction of a skeleton dissertation with the required
    structure. This involves writing the Makefile and makeing dummy files for
    the title page, the proforma, chapters 1 to 5, the appendices and the
    proposal.

    \item Filling in the details required in the cover page and proforma.

    \item Writing the contents of chapters 1 to 5, including examples of common
    \LaTeX\ constructs.

    \item Adding a example of how to use floating figures and encapsulated
    postscript diagrams.
  \end{enumerate}

\section*{Success Criterion for the Main Result}

  The project will be a success if I have a completed dissertation with the
  correct chapter titles and I have achieved my other success criterion, which
  is to blah ...

\section*{Possible Extensions}
  {\em Potential further envisaged evaluation metrics or extensions.}

  If I achieve my main result early I shall try the following alternative
  experiment or method of evaluation ...

\section*{Timetable: Workplan and Milestones to be achieved.}

  {\em Perhaps list ten or so  two-week work-packages.}

  Planned starting date is 16/10/2011.

  \begin{enumerate}
    \item {\bf Michaelmas weeks 2-4} Learn to use X. Read book Y. Read papers
    Z.

    \item {\bf Michaelmas weeks 5-6} Do preliminary test of Q.

    \item {\bf Michaelmas weeks 7-8} Start implementation of main task A.

    \item {\bf Michaelmas vacation} Finish A and start main task B.

    \item {\bf Lent weeks 0-2} Write progress report. Generate corpus of test
    examples. Finish task B.

    \item {\bf Lent weeks 3-5} Run main experiments and achieve working
    project.

    \item {\bf Lent weeks 6-8} Second main deliverable here.

    \item {\bf Easter vacation:} Extensions and writing dissertation main
    chapters.

    \item {\bf Easter term 0-2:}  Further evaluation and complete dissertation.

    \item {\bf Easter term 3:} Proof reading and then an early submission so as
    to concentrate on examination revision.
  \end{enumerate}
